---
title: "Analysis So Far"
---

```{r, message=FALSE}
library(vegan)
library(ggplot2)
library(here)
library(tidyverse)
library(microViz)
library(phyloseq)
library(ggtext)

theme_set(theme_minimal())
```

### Data

Reading in data:

```{r fold=TRUE}
data.priming <- read.csv(here("data", "priming_amoA_deltaCt.csv"), header = T) %>% 
  rename(sample_id = X) 

data.raw <- read.csv(here("data", "priming_amoA_rawCt.csv"), header = T) %>% 
  rename(sample_id = X)

data.priming.long <- data.priming %>% 
  pivot_longer(cols = amoA.001:amoA.078, names_to = "amoA", values_to = "deltaCT")

data.raw.long <- data.raw %>% 
  pivot_longer(cols = amoA.001:amoA.078, names_to = "amoA", values_to = "CT")

data.priming.long$sample_id <- fct_reorder(data.priming.long$sample_id, parse_number(data.priming.long$sample_id))

df <- data.priming[, -1]
rownames(df) <- data.priming[, 1]

metadata <- df %>% 
  select(fert_level:field_rep) %>%
  mutate(across(everything(), as.factor))


amoa_counts <- df %>% 
  select(starts_with("amoA"))

```

`data.priming` contains the data for our experiment. There are rows for samples, columns for the 
delta CTs of the different amoAs, and some metadata.

```{r}
data.priming[1:5, 1:5]
```

`data.raw` contains the same columns but lists the raw CT values instead of the 16s-normalized ones.

```{r}
data.raw[1:5, 1:5]
```

THe `long` versions of these dataframes contains the same info but in long format to play nicely
with `ggplot`.

## Removing amoAs

We'll start by removing those amoAs from our data that are not present in over 30 samples across both treatments.

We'll first start by counting the non-detects for each amoA.

```{r}
non_detect_counts <- data.raw.long %>%
  group_by(fert_level, amoA) %>% 
  count(CT == 40) %>% 
  rename(non_detect = `CT == 40`) %>%
  filter(non_detect == TRUE)
```

Finding the amoAs that are not detected in > 30 across both samples

```{r}
removes <- non_detect_counts %>% 
  pivot_wider(names_from = fert_level, values_from = n, names_prefix = "fert.") %>%
  filter(fert.0 > 30 & fert.336 > 30) %>%
  pivot_longer(cols = fert.0:fert.336, names_to = "fert_level", values_to = "n")
```

We'll now reduce `data.priming` by removing those amoAs that are largely non-detects. 
We'll also update the `long` version while we're at it

```{r}
data.priming.reduced <- data.priming %>% 
  select(-one_of(removes$amoA))

data.priming.reduced.long <- data.priming.reduced %>% 
  select(-sample_id, field_rep) %>% 
  pivot_longer(cols = amoA.001:amoA.074) 

```

Here's a barchart of what we're removing:

```{r}
removes %>% 
  mutate(amoA = str_sub(amoA, -3)) %>% 
  mutate(favored = case_when(
    amoA %in% c("006", "038", "064", "069", "071") ~ "Nothing",
    amoA %in% c("021", "028", "030", "048", "073", "075", "076", "077", "078") ~ "Non-fertilized",
    amoA %in% c("040", "050", "053") ~ "Fourth quadrant",
    TRUE ~ "First quadrant"
  )) %>% 
  mutate(fert_level = str_sub(fert_level, start = 6)) %>% 
  ggplot(aes(amoA, n, fill = favored )) +
  geom_col() +
  facet_wrap(~ fert_level) + 
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.text = element_markdown(size = 12),
    legend.title = element_markdown(size = 12, hjust = 0),
    strip.background = element_rect(size = 1, color = "black", fill = "NA"),
    panel.grid = element_line(color = "gray95"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.border = element_rect(color = "black", size = 1, fill = NA)
  ) +
  scale_fill_viridis_d(begin = 0, end = 0.5) +
  scale_y_continuous(limits = c(0, 50), expand = expansion(add = c(0, 0))) +
  scale_x_discrete(limits = rev) + 
  coord_flip() + 
  labs(
    y = "Number of samples with > 30 non-detects",
    title = "Fertilizer level",
    fill = "Favored by..."
  )
```

Note that most of the non-detects that we're removing are from the non-fertilized group.

Next, we'll convert the CT values to presence/absence for use later on.

```{r}
amoA_presence_absence <- data.raw %>% 
  select(sample_id, starts_with("amoA")) %>%
  select(-one_of(removes$amoA)) %>%
  mutate(across(starts_with("amoA"), ~ ifelse(.x == 40, 0, 1))) 
```

## Ordination

Calculating the NMDS (positioning the sites):

```{r, echo=TRUE, results='hide'}
mds.priming = metaMDS(data.priming.reduced %>% select(amoA.001:amoA.074), distance = "bray", k = 3)

site.scores <- as.data.frame(scores(mds.priming, display = "sites")) %>% 
  mutate(sample_id = data.priming.reduced$sample_id,
         Crop = data.priming.reduced$crop,
         Fert_Level = as.factor(data.priming.reduced$fert_level),
         Day = as.factor(data.priming.reduced$doe),
         Substrate_Addition = as.factor(data.priming.reduced$addition))
```

This is enough to plot the NMDS:

```{r}
nmds.plot <- site.scores %>% 
  ggplot(aes(NMDS1, NMDS2, fill = Fert_Level)) +  
  geom_hline(yintercept = 0.0,
             colour = "grey",
             lty = 2) +
  geom_vline(xintercept = 0.0,
             colour = "grey",
             lty = 2) +
  geom_point(aes(shape = Crop), size = 4) + 
    theme(
    plot.title = element_text(hjust = 0.5),
    legend.text = element_markdown(size = 12),
    legend.title = element_markdown(size = 12, hjust = 0),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    panel.grid = element_line(color = "gray95"),
    panel.border = element_rect(color = "black", size = 1, fill = NA)
  ) +
  scale_fill_discrete(name = "Fertilizer Level<br>
                              <span style = 'font-size:8pt;'>
                              (kg N ha<sup>-1</sup> y<sup>-1</sup>)
                              </span>") +
  scale_shape_manual(labels = c("Corn", "*Miscanthus<br>Gigantus*"),
                     values = c(21, 24)) +
  guides(
    fill = guide_legend(override.aes = list(shape = 22, size = 5)),
    shape = guide_legend(title = "Crop", override.aes = list(shape = c(16, 17)))
  )  
```

We can also add ellipses to it if you're interested in that:

```{r}
nmds.plot +
  stat_ellipse(aes(color = Fert_Level), size = 1, linetype = "dashed", show.legend = FALSE) 
```

And again with shading:

```{r}
nmds.plot +
  stat_ellipse(aes(color = Fert_Level), size = 1, linetype = "dashed", show.legend = FALSE) +
    stat_ellipse(aes(fill = Fert_Level), size = 1, linetype = "dashed", show.legend = FALSE, geom = "polygon", alpha = 0.1) 
```

## Statistics

### Which factors have an impact on overall community composition?

```{r}
X <- data.priming.reduced %>% 
  select(-c(amoA.001:amoA.074))
Y <- data.priming.reduced %>% 
  select(c(amoA.001:amoA.074))

adonis(Y ~ X$fert_level + X$addition + X$crop + X$timepoint) 
```

This tells us that fertilization level is very significant and explains ~37% of the variation
in our samples. Crop is also a significant factor on community composition, though it only explains
2.3% of the variation.

### How do the treatment factors affect the "abundance" of genes on an individual level?

All the code below does is perform an ANOVA of the gene's abundance against all the terms
and all of their interactions.

```{r}
formulae <- lapply(colnames(data.priming.reduced %>% select(amoA.001:amoA.074)), function(x) as.formula(paste0(x, " ~ fert_level * crop * timepoint * addition")))

res <- lapply(formulae, function(x) broom::tidy(aov(x, data = data.priming.reduced)))
names(res) <- format(formulae)
names(res) <- str_sub(names(res), end = 8)

anova_results <- lapply(seq_along(res), function(i) res[[i]] %>% mutate(gene = names(res)[[i]])) %>% 
  bind_rows() %>% 
  filter(term != "Residuals") %>% 
  mutate(sig = case_when(
    p.value < 0.05 & p.value > 0.01 ~ "*",
    p.value < 0.01 & p.value > 0.001 ~ "**",
    p.value < 0.001 ~ "***",
    TRUE ~ "NS"
  ))
```

Visualization:

```{r}
anova_results %>% 
  mutate(gene = str_sub(gene, -3)) %>% 
  ggplot(aes(gene, term, fill = sig)) + 
  geom_tile(color = "black") + 
  coord_equal() + 
  labs(y = "",
       x = "amoA",
       title = "Summary of ANOVA results",
       fill = "Significance ") + 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)
  ) + 
  scale_fill_viridis_d(option = "magma", direction = -1)
```

Overall, we see that, again, fertilization level has a significant impact on abundance levels of the individual genes, 
and it's not even really that close.. There are other factors that might be worth investigating on a gene-by-gene basis, 
too, but that's for later.

## Biodiversity

Let's start by visualizing the presence/absence table:

```{r}
amoA_presence_absence %>% 
  pivot_longer(cols = amoA.001:amoA.074, names_to = "amoA", values_to = "presence") %>% 
  mutate(amoA = str_sub(amoA, -3),
         presence = as.factor(presence)) %>% 
  left_join(metadata %>% rownames_to_column(var = "sample_id")) %>% 
  ggplot(aes(sample_id, amoA, fill = presence)) + 
  geom_tile(color = "black") +
  labs(
    x = "",
    y = "",
    fill = "Species is...",
    title = "Presence/absence of species in crop priming samples",
    subtitle = "(separated by fertilization level)"
  ) + 
  scale_fill_viridis_d(labels = c("Absent", "Present"),
                       begin = 0, end = 1,
                       option = "magma") +
  theme(
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    strip.text = element_text(size = 10, face = "bold")
  ) + 
  scale_y_discrete(limits = rev) + 
  facet_wrap(~ fert_level, scales = "free")
```

## Reading in the best BLAST hit info:

```{r}
amoA_organism_info <- readxl::read_xlsx(here("data", "amoa_mfp_qpcr_org_accessions.xlsx"), sheet = 5) %>% 
  select(-c(contains(c("forward", "reverse", "notes")))) 
```

Counts of best BLAST hits:

```{r}

amoA_organism_info %>% 
  count(best_blast_hits, sort = TRUE) 

```


## Creating a phyloseq object


```{r other-error-chunk, message=FALSE, warning=FALSE}
amoa_tax_table <- amoA_organism_info %>% 
  select(array_name, best_blast_hits) %>% 
  column_to_rownames(var = "array_name") %>% 
  tax_table()

rownames(amoa_tax_table) <- amoA_organism_info$array_name
```


```{r error-chunk}
ps <- phyloseq(
  otu_table(amoA_presence_absence %>% column_to_rownames(var = "sample_id"), taxa_are_rows = FALSE),
  sample_data(metadata),
  amoa_tax_table
)

```

## Richness analysis

How does observed richness and evenness change with treatment level? This is a modified diversity function
that does a bunch of nice stuff that `phyloseq::estimate_richness` doesn't do.

```{r, fold=TRUE}
estimate_richness_mod <- function(physeq, split=TRUE, measures=NULL){
  

  if( !split ){
    OTU <- taxa_sums(physeq)		
  } else if( split ){
    OTU <- as(otu_table(physeq), "matrix")
    if( taxa_are_rows(physeq) ){ OTU <- t(OTU) }
  }
  

  renamevec = c("Observed", "Chao1", "ACE", "Shannon", "Pielou", "Simpson", "InvSimpson", "SimpsonE", "Fisher")
  names(renamevec) <- c("S.obs", "S.chao1", "S.ACE", "shannon", "pielou", "simpson", "invsimpson", "simpsone", "fisher")

  if( is.null(measures) ){
    measures = as.character(renamevec)
  }

  if( any(measures %in% names(renamevec)) ){
    measures[measures %in% names(renamevec)] <- renamevec[names(renamevec) %in% measures]
  }
  

  if( !any(measures %in% renamevec) ){
    stop("None of the `measures` you provided are supported. Try default `NULL` instead.")
  }
  

  outlist = vector("list")

  estimRmeas = c("Chao1", "Observed", "ACE")
  if( any(estimRmeas %in% measures) ){
    outlist <- c(outlist, list(t(data.frame(estimateR(OTU)))))
  }
  if( "Shannon" %in% measures ){
    outlist <- c(outlist, list(shannon = diversity(OTU, index="shannon")))
  }
  if( "Pielou" %in% measures){
    #print("Starting Pielou")
    outlist <- c(outlist, list(pielou = diversity(OTU, index = "shannon")/log(estimateR(OTU)["S.obs",])))
  }
  if( "Simpson" %in% measures ){
    outlist <- c(outlist, list(simpson = diversity(OTU, index="simpson")))
  }
  if( "InvSimpson" %in% measures ){
    outlist <- c(outlist, list(invsimpson = diversity(OTU, index="invsimpson")))
  }
  if( "SimpsonE" %in% measures ){

    outlist <- c(outlist, list(simpsone = diversity(OTU, index="invsimpson")/estimateR(OTU)["S.obs",]))
  }
  if( "Fisher" %in% measures ){
    fisher = tryCatch(fisher.alpha(OTU, se=TRUE),
                      warning=function(w){
                        warning("phyloseq::estimate_richness: Warning in fisher.alpha(). See `?fisher.fit` or ?`fisher.alpha`. Treat fisher results with caution")
                        suppressWarnings(fisher.alpha(OTU, se=TRUE)[, c("alpha", "se")])
                      }
    )
    if(!is.null(dim(fisher))){
      colnames(fisher)[1:2] <- c("Fisher", "se.fisher")
      outlist <- c(outlist, list(fisher))
    } else {
      outlist <- c(outlist, Fisher=list(fisher))
    }
  }
  out = do.call("cbind", outlist)

  namechange = intersect(colnames(out), names(renamevec))
  colnames(out)[colnames(out) %in% namechange] <- renamevec[namechange]

  colkeep = sapply(paste0("(se\\.){0,}", measures), grep, colnames(out), ignore.case=TRUE)
  out = out[, sort(unique(unlist(colkeep))), drop=FALSE]

  out <- as.data.frame(out)
  return(out)
}
```


```{r}
metrics <- c("Observed", "Shannon")
richness <- estimate_richness_mod(ps, measures = metrics) %>% 
  rownames_to_column(var = "sample_id") %>% 
  mutate(sample_id = str_sub(sample_id, start = 2)) 
```


```{r}
richness <- left_join(sample_data(ps) %>% data.frame() %>% rownames_to_column(var = "sample_id"), richness) %>% 
  pivot_longer(cols = Observed:Shannon, names_to = "Metric", values_to = "Value")
```

### Statistical tests

Significance test of fertilization level on richness.

```{r}
(sig_rich_fert <- kruskal.test(Value ~ fert_level, data = richness %>% filter(Metric == "Observed")))
```

The `p-value < 0.001` gives us strong statistical evidence that richness is significantly different between 
fertilization treatment groups.


Significance test of fertilization level on richness

```{r}
(sig_even_fert <- kruskal.test(Value ~ fert_level, data = richness %>% filter(Metric == "Shannon")))
```

The `p-value < 0.001` gives us strong statistical evidence that Shannon diversity is significantly different between 
fertilization treatment groups.

## Making nice plots for stat differences

Standard deviations, mean

```{r}
summaries <- richness %>% 
  group_by(Metric, fert_level) %>% 
  summarize(mean_val = mean(Value), 
            sd_val = sd(Value) / 4,
            .groups = "drop") 
```


```{r}
this_annotation <- data.frame(
  Metric = c("Observed", "Shannon"),
  lab = c("***", "***"),
  x = 1.5,
  y = c(50 + 5, 4 + 0.5),
  lineheights = c(50 + 2, 4 + 0.25)
)

summaries %>%  
  ggplot(aes(fert_level, mean_val, fill = fert_level)) + 
  geom_col(color = "black", size = 1) +
  facet_wrap(~ Metric, scales = "free_y") + 
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    axis.title.y = element_blank(),
    strip.placement = "outside",
    plot.title = element_text(hjust = 0.5),
    strip.text.y = element_text(face = "bold", size = 10),
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_line(color = "gray90", linetype = "dashed"),
    axis.ticks = element_blank(),
    panel.border = element_rect(color = "black", size = 1, fill = "NA")
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  geom_errorbar(aes(ymin = mean_val - sd_val, ymax = mean_val + sd_val, width = 0.5)) + 
  geom_text(
    data = this_annotation,
    aes(x = x, y = y, label = lab),
    inherit.aes = FALSE,
    size = 5
    ) + 
  geom_segment(data = this_annotation,
               aes(x = 1,
                   xend = 2, 
                   y = lineheights,
                   yend = lineheights),
               inherit.aes = FALSE) + 
  labs(
    x = "Fertilization Level\n(*** = p < 0.001 by Kruskal Wallis)",
    title = "Alpha diversity metrics by fertilization level"
    
  )

```

## Beta diversity

We'll start beta diversity analysis off by doing an ADONIS/PERMANOVA to determine if 
treatment centroids/treatment variations are different between groups. 

```{r}
dis <- vegdist(otu_table(ps))
groups <- sample_data(ps)$fert_level
mod <- betadisper(dis, groups)
anova(mod)
```

Since `p <<<< 0.0001`, there is strong evidence that the overall community compositions
are significantly different (treatment centroid, distance to centroid, community variation)
between the two groups. W can visualize this with a 1 SD ellipse:

```{r}
plot(mod, ellipse = TRUE, hull = FALSE) 
```

We see that there is clear separation between the two treatment centroids. Let's do some more analysis on the 
distance-to-centroids that we're seeing:

```{r}
betadistances <- data.frame(
  time_frame = mod$group,
  distance = mod$distances
)

betadistances %>% 
  ggplot(aes(time_frame, distance)) + 
  geom_boxplot(size = 1, outlier.shape = NA) + 
  geom_jitter(aes(fill = time_frame), size = 5, shape = 21, width = 0.2) +
  theme(
    legend.position = "none",
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    # panel.grid.major.y = element_line(color = "gray", linetype = "dashed"),
    plot.title = element_text(size = 17),
    plot.subtitle = element_text(size = 9),
    axis.ticks.length = unit(0.25, "cm"),
    # axis.ticks.x = element_line(color = "gray", size = 0.25),
    axis.ticks.x = element_blank(),
    axis.text.x = element_text(face = "bold", angle = 0, size = 12),
    panel.border = element_rect(color = "black", size = 1, fill = NA),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 14, face = "bold"),
    # legend.position = "none"
    
  ) + 
  labs(
    color = "",
    y = "Distance to centroid"
  ) +
  ggsignif::geom_signif(
    map_signif_level = TRUE,
    comparisons = list(c("0", "336")),
    test = "t.test",
    step_increase = 0.1,
    color = "black",
    size = 1,
    textsize = 5,
    tip_length = 0
  )
```


The significance bar is coming from the PERMANOVA test we did above. We see that there is actually
less beta diversity (as meaasured by distance-to-centroid) in the fertilized group than in the non-
fertilized group. We'll see another visualization backing this up in the next section:

## Composition

Let's visualize the composition of the communities, separated by fertilization. We'll start with
raw counts - how many times was that best BLAST hit seen in that sample?

```{r}
comp_barplot(ps, "ta1",
             facet_by = "fert_level",
             sample_order =  "default",
             tax_transform_for_plot = "identity") +
  coord_flip() + 
  labs(
    title = "Sample composition by fertilization level",
    subtitle = "(raw counts)"
  ) + 
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_text(margin = margin(r = -7)),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, size = 10),
    strip.text = element_text(size = 10, face = "bold")
  ) +
  guides(
    fill = guide_legend(title = "Best BLAST hit", reverse = TRUE)
  )

```

We see that overall the fertilized group appears to have more richness in it.

How about sample composition? IE, relative abundances?

```{r}
comp_barplot(ps, "ta1",
             facet_by = "fert_level",
             sample_order =  "default") +
  coord_flip() + 
  labs(
    title = "Sample composition by fertilization level",
    subtitle = "(relative abundance)"
  ) + 
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_text(margin = margin(r = -7)),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, size = 10),
    strip.text = element_text(size = 10, face = "bold")
  ) +
  guides(
    fill = guide_legend(title = "Best BLAST hit", reverse = TRUE)
  )
```

Two big things pop out:

* species distribution is more even in the fertilized group. This makes sense given previous results
showing that Shannon entropy is higher and beta diversity is lower in the fertilized group. You can also 
see that the communities just look more like each other in the fertilized group, which manifests in shorter
distance-to-centroids/lower community variation.
* There's more green in the fertilized group.

## Statistics on a best BLAST hit level

The next chunk is just doing some data transformation stuff to count the number of times
each organism was seen in each sample in preparation for the statistical analysis.

```{r}
pa_count <- ps %>% 
  otu_table() %>%
  data.frame %>%
  rownames_to_column(var = "sample_id") %>% 
  pivot_longer(amoA.001:amoA.074) 


org_table <- tax_table(ps) %>% 
  data.frame %>% 
  rownames_to_column(var = "name") %>% 
  rename(bbh = ta1) %>% 
  mutate(cleaned_names = janitor::make_clean_names(bbh))

bbh_sample_counts <- left_join(pa_count, org_table, by = "name") %>%
  group_by(sample_id, bbh) %>% 
  summarize(value = sum(value)) %>% 
  pivot_wider(names_from = "bbh", values_from = value)

bbh_level_counts <- left_join(bbh_sample_counts,
          sample_data(ps) %>% 
            data.frame %>% 
            rownames_to_column(var = 'sample_id') %>% 
            right_join(bbh_sample_counts)
) %>% 
  ungroup()

bbh_level_counts %>% 
  pivot_longer(cols = 2:22) 
  
```

Here, we're preparing formulas to feed to a `lapply` function to perform a Kruskal-Wallis test on 
all of the organisms.

```{r}
formulae <- lapply(colnames(bbh_sample_counts %>% select(-sample_id) %>% janitor::clean_names()) , function(x) as.formula(paste0(x, " ~ fert_level * crop * timepoint * addition")))

formulae[[1]] <- NULL

res <- lapply(formulae, function(x) broom::tidy(aov(x, data = bbh_level_counts %>% janitor::clean_names())))
names(res) <- format(formulae)
names(res) <- lapply(names(res), function(x) str_split(x, "~")[[1]][1]) %>% unlist()

anova_results.counts <- lapply(seq_along(res), function(i) res[[i]] %>% mutate(gene = names(res)[[i]])) %>% 
  bind_rows() %>% 
  filter(term != "Residuals") %>% 
  mutate(gene = str_trim(gene))
```

Visualizing the results again:

```{r}
anova_results.counts %>%
  left_join(org_table, by = c("gene" ="cleaned_names")) %>%
  mutate(sig = case_when(
    p.value < 0.05 & p.value > 0.01 ~ "*",
    p.value < 0.01 & p.value > 0.001 ~ "**",
    p.value < 0.001 ~ "***",
    TRUE ~ "NS"
  )) %>% 
  ggplot(aes(term, bbh, fill = sig)) + 
  geom_tile(color = "black") + 
  labs(y = "",
       x = "",
       title = "Summary of ANOVA results",
       fill = "Significance ") + 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    axis.text.y = element_text()
  ) + 
  scale_fill_viridis_d(option = "magma", direction = -1) + 
  scale_y_discrete(limits = rev) +
  coord_equal() 
```

We see the same pattern at the organism level as when we did this at the gene level:
fertilization level is by far the most significant factor affecting Presence/Absence of 
organisms.
